Deciding to Disclose

### 2015-09-15 Conclusion.tex
Inter-intra distinction

From a pragmatic perspective, the differing response characteristics of the decision rules are substantial and significant. The lack of a mechanism of homophily in the very simple rules leads to a high level of uncertainty in the overall dynamics, since even irrelevant information is taken at face value and to be equally valuable. By contrast, the belief structure of the \ac{CPT}, and Bayesian models represents a useful abstraction which allows the use of the relevant aspects of the information.  Naturally, incorporating homophily, by, for example weighting shared information by the type of the sharer, would represent a trivial modification to the heuristic models. While to some extent this highlights the flexibility of the decision rule approach, it would of course sacrifice the parsimony of the model. This is an important consideration, given that part of the argument in favour of a decision theoretic approach lies in the minimal nature of the behavioural rules, which can be seen as occupying a middle ground between parameter and model.

One of the notable features of the results is the similarity in behaviour of the two classes of decision rule. To some extent this reflects poorly on the most complex rule, \ac{CPT}, which diverges only minimally in behaviour from the Bayesian model. This might be to a degree anticipated, in that the payoffs are unrealistic, which limits the utility of the \ac{CPT} approach.  Additionally, work by \citet{Glockner2012} has shown that there is considerable variation in individual parameters for the decision model, whereas we have let them remain homogeneous here. In the same vein, utility functions should arguably vary between individual agents, which could potentially be addressed by replacing the fixed payoffs used here with a distribution.  With this said, the significant increase in complexity, which entails both additional parameters and increases to simulation time may auger for a middle ground, particularly where elicitation of payoffs is impractical.  This, together with the variability associated with the heuristic type decision rules speaks to a trade off between capturing reality, and replicating it.

@@

In reality it might be anticipated that midwives would not withhold judgement, and would pass on concerns about specific women to their colleagues, or that particularly dramatic stories would persist and be passed. This might be addressed by incorporating noisy type information \citep{Feltovich2002}, capturing the unintentional information transmitted during appointments, together with a relaxation of the assumptions about when information may be shared and more sophisticated model of information transmission in general. This also highlights an advantage of the \ac{BACCO} approach, in diagnosing issues with model design by giving insight into parameters which are contributing inappropriately to variance in output. Coupled with the ability of emulators to rapidly explore parameter space, this clearly suggests that statistical emulation is a powerful tool to support simulation based approaches.

>>>>

From a pragmatic perspective, the differing response characteristics of the classes decision rules are substantial and significant. The lack of a mechanism of homophily in the very simple rules leads to a high level of uncertainty in the overall dynamics, since even irrelevant information is taken at face value and to be equally valuable. By contrast, the belief structure of the \ac{CPT}, and Bayesian models represents a useful abstraction which allows the use of the relevant aspects of the information.  Naturally, incorporating homophily, by, for example weighting shared information by the type of the sharer, would represent a trivial modification to the heuristic models. While to some extent this highlights the flexibility of the decision rule approach, it would of course sacrifice the parsimony of the model. This is an important consideration, given that part of the argument in favour of a decision theoretic approach lies in the minimal nature of the behavioural rules, which can be seen as occupying a middle ground between parameter and model.

One of the notable features of the results is that the behaviour of rules within a class is very similar. To some extent this reflects poorly on the most complex rule, \ac{CPT}, which diverges only minimally in behaviour from the Bayesian model. This might be to a degree anticipated, in that the payoffs are unrealistic, which limits the utility of the \ac{CPT} approach.  Additionally, work by \citet{Glockner2012} has shown that there is considerable variation in individual parameters for the decision model, whereas we have let them remain homogeneous here. In the same vein, utility functions should arguably vary between individual agents, which could potentially be addressed by replacing the fixed payoffs used here with a distribution.  With this said, the significant increase in complexity, which entails both additional parameters and increases to simulation time may auger for a middle ground, particularly where elicitation of payoffs is impractical.  This, together with the variability associated with the heuristic type decision rules speaks to a trade off between capturing reality, and replicating it.

@@

In reality it might be anticipated that midwives would not withhold judgement, and would pass on concerns about specific women to their colleagues, or that particularly dramatic stories would persist and be passed. This might be addressed by incorporating noisy type information \citep{Feltovich2002}, capturing the unintentional information transmitted during appointments, together with a relaxation of the assumptions about when information may be shared and more sophisticated model of information transmission in general. This also highlights an advantage of the \ac{BACCO} approach (which we describe in section \ref{sub:sensitivity}), in diagnosing issues with model design by giving insight into parameters which are contributing inappropriately to variance in output. Coupled with the ability of emulators to rapidly explore parameter space, this clearly suggests that statistical emulation is a powerful tool to support simulation based approaches.
